Policy Implications of Coupled Economic and Ecological Dynamics in Aquatic Systems

### 2022-11-17 README.Rmd
updating renv instructions

>>>>

## renv

This repository is equipped with [`renv`](https://rstudio.github.io/renv/) for package management.

To install all dependencies for this project

1. Open R

2. Make sure you have `renv` installed (if not, `install.packages("renv")`)

3. Inside R, making sure the working directory is set to the root directory of this repository, run `renv::restore()`

4. Follow all prompts. This will install local versions of all the dependencies needed for this project

5. If you have trouble installing `marlin`, see instructions [here](https://danovando.github.io/marlin/#installation-troubleshooting)
